### 2009-04-27 doc/internal_notes/UnicoreSupport/UnicoreSupport.tex
Starting cleaning up documentation

Currently it is possible to use the \texttt{arcsub, arcstat} and \texttt{arcinfo} commands, though with some limited functionality (it is not possible to upload input files and the returned job/cluster job information is sparse).

>>>>

Currently it is possible to use the \texttt{arcsub, arcstat, arcinfo} and \texttt{arckill} commands, though with some limited functionality (it is not possible to upload input files and the returned job/cluster job information is sparse).
